---
title: "PAM Clustering"
author: "Carlsberg A1"
date: "21/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup library, include = FALSE}
library(dplyr)
library(tidyverse)
library(car)
library(ggplot2)
library(lubridate)
library(readxl)
library(janitor)
library(GGally)
library(ggthemes)
library(cluster)
library(Hmisc)
library(factoextra)
library(Rtsne)
library(kmed)
```

## Load the dataset
```{r load the library, message = FALSE, warning = FALSE}
#customer <- read_xlsx('newest_customer.xlsx')
setwd("/Users/suzi/Desktop/Term1 - LBS/LAB/7th_week_work")
customer <- read_xlsx('20200523_customer.xlsx')
```

## Multicollinearity check
```{r}
customer %>% 
  select(-starts_with('b'), -c(1:30)) %>% 
  ggcorr(method = c("pairwise", "pearson"), layout.exp = 3, label_round=1, label = TRUE,label_size = 2, hjust = 1)
```

## Data Preparation
```{r dataset preparation, message = FALSE, warning = FALSE}
#prepare the dataset for the clustering
cust_df <- customer %>%
    select(avg_con_monthly, ci_craft_prop_beers, ci_craft_prop_con, ci_lager_prop_beers, ci_lager_prop_con, ci_specialties_prop_beers, ci_specialties_prop_con, number_of_brands, med_income, total_pop_in_city, sd, male_perc, he_she_consumes_beer_everyday, glasses_of_wine_a_day, persons_aged_11_years_and_over_who_consume_beer, everyday_social_per_100, never_social_per_100, rating, center_or_not, c(near_basketball:near_university), outdoor_seating, main_classification, -near_football) %>% 
  drop_na()

cust_df$center_or_not <- as.factor(cust_df$center_or_not)
cust_df$main_classification <- as.factor(cust_df$main_classification)
cust_df$near_basketball <- as.factor(cust_df$near_basketball)
cust_df$near_cinema <- as.factor(cust_df$near_cinema)
cust_df$near_neighborhood <- as.factor(cust_df$near_neighborhood)
cust_df$near_shopping <- as.factor(cust_df$near_shopping)
cust_df$near_theatre <- as.factor(cust_df$near_theatre)
cust_df$near_tourist <- as.factor(cust_df$near_tourist)
cust_df$near_university <- as.factor(cust_df$near_university)
cust_df$outdoor_seating <- as.factor(cust_df$outdoor_seating)
cust_df$rating <- as.numeric(cust_df$rating)

#scale the numbers for the sake of visualisation of numerical variables
cust_df[,1:18] <- scale(cust_df[,1:18])
```

## Silhouette Analysis (decide # of clusters)
```{r Silhouette, message = FALSE, warning = FALSE}
dist <- daisy(cust_df, metric = c("gower"))

sil_width <- c(NA)
for(i in 2:8){  
  pam_fit <- pam(dist, diss = TRUE, k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}
plot(1:8, sil_width,
     xlab = "Number of clusters",
     ylab = "Silhouette Width")
lines(1:8, sil_width)
```

## Gower distance - without city (using proxy - number of populations)
```{r PAM, message = FALSE, warning = FALSE}
pam <- pam(dist, diss = T,2)
sil <- silhouette(pam$clustering, dist)
plot(sil)

pam_results <- cust_df %>%
  mutate(cluster = pam$clustering) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))

pam_results$the_sumrye
```

## PAM (k=2) - graphics
```{r visualisation, message = FALSE, warning = FALSE}
tsne_obj <- Rtsne(dist, is_distance = TRUE)

tsne_data <- tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam$clustering))

ggplot(aes(x = X, y = Y), data = tsne_data) +
  geom_point(aes(color = cluster))
```

## PAM (k=2) - graphics (only with numeric variables)
```{r visualisation2, message = FALSE, warning = FALSE}
cust_df$cluster <- as.factor(pam$clustering)
center_locations <- cust_df[,c(1:18,29)] %>% filter(!is.na(rating)) %>% group_by(cluster) %>% summarize_all(mean)
temp <- center_locations %>% gather(key = 'variable', value = 'value', -cluster, factor_key = TRUE)

pam2_gg <- temp %>% 
  ggplot(aes(x = variable, y = value, order = cluster))+
  geom_line(aes(color = cluster, group = cluster), linetype = 'dashed', size = 1)+
  geom_point(size = 2, shape = 4)+
  ggtitle("PAM K = 2")+
  labs(fill = 'cluster')+
  theme(text = element_text(size=10),axis.text.x = element_text(angle=45, hjust=1),legend.title=element_text(size=5),legend.text = element_text(size=5))+
  scale_color_manual(values = c("green", "orange", "red", "blue","purple"))

pam2_gg
```

## Feature Importance (k=2)
```{r feature importance 1}
cust_df <- as.data.frame(cust_df)
barplotnum(cust_df[,1:17], pam$clustering, alpha = 0.05)
```

# 5 Clusters
## Gower distance - without city (using proxy - population #)
```{r 5 clusters - silhouette plot and summary}
pam5 <- pam(dist, diss = T,5)
sil5 <- silhouette(pam5$clustering, dist)
plot(sil5)

pam_results5 <- cust_df %>%
  mutate(cluster = pam5$clustering) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))

pam_results5$the_summary
```

## PAM (k=5) - graphics
```{r visualisation1 for 5 segments, message = FALSE, warning = FALSE}
tsne_obj <- Rtsne(dist, is_distance = TRUE)

tsne_data <- tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam5$clustering))

ggplot(aes(x = X, y = Y), data = tsne_data) +
  geom_point(aes(color = cluster))
```

## PAM (k=5) - graphics (only with numeric variables)
```{r visualisation2 for 5 segments, message = FALSE, warning = FALSE}
cust_df$cluster5 <- as.factor(pam5$clustering)
center_locations <- cust_df[,c(1:18,30)] %>% filter(!is.na(rating)) %>% group_by(cluster5) %>% summarize_all(mean)
temp <- center_locations %>% gather(key = 'variable', value = 'value', -cluster5, factor_key = TRUE)

pam5_gg <- temp %>% 
  ggplot(aes(x = variable, y = value, order = cluster5))+
  geom_line(aes(color = cluster5, group = cluster5), linetype = 'dashed', size = 1)+
  geom_point(size = 2, shape = 4)+
  ggtitle("PAM K = 5")+
  labs(fill = 'cluster5')+
  theme(text = element_text(size=10),axis.text.x = element_text(angle=45, hjust=1),legend.title=element_text(size=5),legend.text = element_text(size=5))+
  scale_color_manual(values = c("green", "orange", "red", "blue","purple"))

pam5_gg
```

## Feature Importance (k=5)
```{r feature importance 2}
cust_df <- as.data.frame(cust_df)
barplotnum(cust_df[,1:17], pam5$clustering, alpha = 0.05)
```
